### 2021-03-04 text/draft.tex
metrics per department

The metrics used for the assessment are precision, recall and F1 score.
Precision and recall are standard metrics for indexing quality (e.g.,
Gantert 2016, 197) whereby the F1 score plays are more prominent role in
the assessment of machine indexing (e.g., Suominen 2018, 11--14; Toepfer
and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
(such as indexing consistency, transparency, reproducability) that are
neglected here.

@@

The above scoring metrics were implemented using the scikit-learn
machine learning library (Pedregosa et al. 2011). It is important to
note that each metric comes in three different flavors dubbed ``macro,''
``micro,'' and ``weighted'' respectively. In the macro flavor, the
metric represents simply the mean per class (i.e., correct or incorrect
suggestion). The weighted metric is the macro metric but each class is
weighted by its true positives. By contrast, a metric with the micro
flavor is computed globally over all true positives and false positives
respectively negatives.

@@

In this section, I will assess the perfomance of Annif versus the native
gold standard.

@@

Combining these parameters, we really have 100 Annif configurations
whose perfomance we want to compare and assess: Annif project \(*\) text
base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).

For each configuration, the F1-score (macro, micro and weighted) was
computed. To do so, we call \texttt{\_Analysis.super\_make\_metrics} on
\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
specifies the Annif configuration; a single file for analysis is saved
as \texttt{/analysis/metrics.json}:

@@

\leavevmode\hypertarget{ref-Pedregosa.2011}{}%
Pedregosa, F., G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O.
Grisel, M. Blondel, et al. 2011. {``Scikit-Learn: Machine Learning in
Python.''} \emph{Journal of Machine Learning Research}, no. 12:
2825--30.
\url{https://www.jmlr.org/papers/volume12/pedregosa11a/pedregosa11a.pdf?source=post_page---------------------------}.

@@

>>>>

The metrics used for the assessment are precision, recall and F1-score.
Precision and recall are standard metrics for indexing quality (e.g.,
Gantert 2016, 197) whereby the F1 score plays are more prominent role in
the assessment of machine indexing (e.g., Suominen 2018, 11--14; Toepfer
and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
(such as indexing consistency, transparency, reproducability) that are
neglected here.

@@

The above scoring metrics were implemented using the scikit-learn
machine learning library (Pedregosa et al. 2011). For a given Annif
configuration
(\protect\hyperlink{annif-versus-native-gold-standard}{section ``Annif
versus native gold standard''})\ldots{} {[}perhaps explain how it is
done, important to mention transformation of multilabel to binary{]}.
Note that while

@@

In this section, I will assess the performance of Annif versus the
native gold standard.

@@

Combining these parameters, we really have 100 Annif configurations
whose performance we want to compare and assess: Annif project \(*\)
text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).

For each configuration, the F1-score was then computed. It is important
to note that each metric comes in three different flavors dubbed
``macro,'' ``micro,'' and ``weighted'' respectively (see Sokolova and
Lapalme 2009). In the macro flavor, the metric represents simply the
mean per class (i.e., correct or incorrect suggestion). The weighted
metric is the macro metric but each class is weighted by its true
positives. By contrast, a metric with the micro flavor is computed
globally over all true positives and false positives respectively
negatives. So the ``macro'' and ``weighted'' flavors are useful for
assessing the performance of a configuration with respect to individual
cases of assigning subject terms whereas the ``micro'' flavor is most
suitable to assess the overall performance of a configuration with
respect to assigning subject terms.

To compute the F1-score, we call
\texttt{\_Analysis.super\_make\_metrics} on
\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
specifies the Annif configuration; a single file for analysis is saved
as \texttt{/analysis/metrics.json}:

@@

\leavevmode\hypertarget{ref-Pedregosa.2011}{}%
Pedregosa, F., G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O.
Grisel, M. Blondel, et al. 2011. {``Scikit-Learn: Machine Learning in
Python.''} \emph{Journal of Machine Learning Research}, no. 12:
2825--30.
\url{https://www.jmlr.org/papers/volume12/pedregosa11a/pedregosa11a.pdf}.

@@

\leavevmode\hypertarget{ref-Sokolova.2009}{}%
Sokolova, Marina, and Guy Lapalme. 2009. {``A Systematic Analysis of
Performance Measures for Classification Tasks.''} \emph{Information
Processing {\&} Management} 45 (4): 427--37.
\url{https://doi.org/10.1016/j.ipm.2009.03.002}.
